Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-14 paper/ms.tex
Added some asteroseismology references

The asteroseismic oscillations of thousands of stars were measured using light
curves from the \kepler\ mission (\dfmtodo{cite}) and asteroseismology is a
key science driver for many of the upcoming large scale photometric surveys
(\dfmtodo{cite}).
Most asteroseismic analyses have been limited to relatively high
signal-to-noise oscillations because the standard methods based on statistics
of the empirical periodogram of the data cannot be used to formally propagate
the measurement uncertainties to the constraints on physical parameters
(\dfmtodo{CITE}) and more sophisticated methods are computationally expensive
and they scale poorly to the current state-of-the-art datasets (\dfmtodo{CITE
Brewer etc.}).

>>>>

The asteroseismic oscillations of thousands of stars were measured using light
curves from the \kepler\ mission \citep{Gilliland:2010,Chaplin:2011,Chaplin:2013,Stello:2013}
and asteroseismology is a
key science driver for many of the upcoming large scale photometric surveys
\citep{Campante:2016,Rauer:2014,Gould:2015}.
Most asteroseismic analyses have been limited to relatively high
signal-to-noise oscillations because the standard methods based on statistics
of the empirical periodogram of the data cannot be used to formally propagate
the measurement uncertainties to the constraints on physical parameters
(\dfmtodo{CITE}) and more sophisticated methods are computationally expensive
and they scale poorly to the current state-of-the-art datasets (\dfmtodo{CITE
Brewer etc.}).
